Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-08-13 demystify.tex
updates

\paragraph{Should I ask for feedback?}
No, don't bother.  You will likely not get any useful feedback.  We are not willing (allowed) to reveal your evaluation results or give you advice on how to improve your profile. So just move on.  If you really want feedback, ask your professors, collaborators, ref writers, or those who have previously applied.

>>>>

\paragraph{Should I ask for feedback?}
No, don't bother.  You will likely not get any useful feedback.  We are not willing (somtimes allowed) to reveal your evaluation results or give you feedback on how to improve your profile. \emph{So just move on}.  If you really want advice, ask your professors, collaborators, ref writers, or those who have previously applied.
